---
title: "Finite Sequential Experiments: The Minority Perspective"
subtitle: "A thesis created for the degree of Master of Science in Applied statistics"
author: "Harel Lustiger"
#date: "22 October, 2015"
output: 
  beamer_presentation:
    includes:
       in_header: presentation_metadata.tex
bibliography: references.bib   
#nocite: | 
#        @Lustiger2016
---


```{r global_options, include=FALSE, echo=FALSE}
Sys.setlocale("LC_TIME", "English")

packages_list = c("knitr","pander")
sapply(packages_list, 
       function(package){
           if(!require(package, character.only=TRUE)) 
               install.packages(package,dep=TRUE)
           require(package, character.only=TRUE)})

opts_chunk$set(fig.width=8, fig.height=4, fig.path='figs/', dev='png', dpi=300, 
               echo=FALSE, warning=FALSE, message=FALSE, results='hide')
```

```{r pandoc_options, include=FALSE, echo=FALSE}
panderOptions('table.split.table', Inf)
panderOptions('digits', 3)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# performance.table <- table(some_table)
# pandoc.table(performance.table, style = "rmarkdown", justify = 'left', 
# caption = 'Performance table') 
```


# Questions met in practical application

1. What method should I use to handle the imbalanced property of the data
    * Active Learning, Undersampling, Oversampling, etc.
2. What active learning technique should I use?
    * Uncertainty sampling, Query by Bagging, Variance Reduction, etc. 
3. What base learner should I use for active learning?
    * SVM, Trees, Logistic Regression?
4. What inducer should I use for the model?
    * Same as the active learning base learner, different, 
    depends on the amount of data?

# The main problems and considerations (sorted by severity) 

1. **No knowledge** about the features set
2. **No data** to make choices
    * Before choosing how to sample the data to label, there is no labeled data to perform cross-validation. 
3. **Inadequate data** to perform cross-validation
    * Insufficient data; if we split imbalanced data into K parts, we are likely to get parts without minority instances.
    * Biased data; if the sample is not representative (say the imbalanced ratio is 1) then the evaluation is unreliable.

## Why Random sampling is not a good idea

1. **Waste of budget**; allocating budget for initial random sample contradicts the purpose of having a model in the first place. 
2. **Cross learning curves**; a learner that perform well a small (randomly chosen) subset of the data, often leads to the wrong choice for a larger dataset [@perlich2003tree].

# Sequential design of experiments

<!---
suppose you have a fixed number of positive instances within the database.
Sometimes this is a reasonable assumption. For example, diabetes is usually a 
lifetime disease where 10% of the population have. Although each year there are
new cases, the rate is small enough to assume that the positive number of 
instances is fixed (needs proof with numbers)
-->


# Classical Design of Experiments

* The design of experiments process must consider the desired information to be gained from the analysis.
* The desired information plays an important role in the design of experiments process and it can be viewed as what drives the conception of the design of experiments.
* What is considered to be useful information is often subject area-specific and can take many forms, some of which include:
    * identifying differences between groups
    * determining effects of and interactions between factors
    * determining factor-level settings to optimize some measure of performance
    * determining the probability of some event given factor-level settings, amongst others

# Optimal design

[@Settles2010 , p.23]

## D-optimality (determinant)

## I-optimality (integrated)






# References